---
title: "Assignment"
author: "LEVIN S"
output: html_document
date: "2022-09-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}


```
1. What happens if you make a scatterplot of class vs drv. Why is the plot not useful?

Ans:The class and drv attributes are categorical. Therefore the plot shows the mapping between these categories.

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = class, y = drv))
```



2.What’s gone wrong with this code? Why are the points not blue?
ggplot(data = mpg) + 
geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))	

Ans:The points are not blue because aesthatic have two parameter so the color parameter is not accept ,so the color parameter should be in outsaid the aesthatic function.below the correct is code:
```{r}
ggplot(data = mpg) + 
geom_point(mapping = aes(x = displ, y = hwy), color = "blue"	)

```



3.A.What happens if you map a aesthetic to something other than a variable name, like aes(colour = displ < 5)? 
Ans:
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, colour = displ < 5))

```

Ans:
B.What does the stroke aesthetic do? What shapes does it work with?

  Ans:The stroke aesthetic  to adjust the object thickness for shapes.
  
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy), stroke=3)
```




4 Read ?facet_wrap. What does nrow do? What does ncol do? What other options control the layout of the individual panels? Why doesn’t facet_grid() have nrow and ncol variables?

Ans:Facet grids do not have these configuration because the rows and cols are determined by the specified attributes.
```{r}
?facet_wrap   
```



5. A)a)	What plots does the following code make? What does do?

  ans:facet_grid() divides the plot in the particular area. That is used to make the plot into subplot.
 
 
```{r}
ggplot(data = mpg) + 
geom_point(mapping = aes(x = displ, y = hwy)) +
facet_grid(drv ~ .)
```


```{r}
ggplot(data = mpg) + 
geom_point(mapping = aes(x = displ, y = hwy)) +
facet_grid(. ~ cyl)                                                                          

```


 
 b)	When using facet_grid() you should usually put the variable with more unique levels in the columns. Why?  
 
 Aans:becasue it  gives meaningful interpretation.
 
 
 6. What geom would you use to draw a line chart? A boxplot? A histogram? An area chart?
 
 ans:
        line chart: geom_line()
        box plot: geom_boxplot()
        histogram: geom_histogram()
        area chart: geom_area()
```{r}
ggplot(data=mpg)+
  geom_boxplot(aes(x=displ,y=hwy))

ggplot(data=mpg)+
  geom_line(aes(x=displ,y=hwy))


ggplot(data=mpg)+
  geom_area(aes(x=displ,y=hwy))

```




        
        
        
7. Will these two graphs look different? Why/why not?

  ans:  No , the two graphs looks similar.Becasue both geom_point() and geom_smooth() use same          data and mappings.see the output,
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
     geom_point() +
     geom_smooth()

```

```{r}
ggplot() +
     geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) +
     geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))


```


      


8. What does geom_col() do? How is different to geom_bar()?

  ans: geom_col() requires both x and y where as geom_bar() requires only x variables.
  
  
  
```{r}
ggplot(data = mpg) +
     geom_col( mapping = aes(x = displ, y = hwy))
```
  
```{r}
ggplot(data = mpg) +
     geom_bar( mapping = aes(x =class))
```



9. What is the default geom associated with stat_summary()? How could you rewrite the previous plot to use that geom function instead of the stat function?
   ans:The geom_pointrange is a default geom associate with stat_summary(),
   
  rewrite the comment is below there:

```{r}
ggplot(data = diamonds) +
  geom_pointrange(mapping = aes(x = cut, y = depth),
                 stat="summary", 
               fun.ymin = min,
               fun.ymax = max,
               fun.y = mean)
```






10. What does the plot below tell you about the relationship between city and highway mpg? Why is coord_fixed() important? What does geom_abline() do?
 
  ans: When city mileage increases hwy mileage also increases. There is a positive relationship between city mileage        and hwy mileage.
      coord_fixed: Adjust the values in the data set.
      geom_abline: Its shows the prediction or regression between x and y.

```{r}
ggplot(data = mpg, mapping =aes(x =cty, y =hwy)) +
geom_point() +
geom_abline() +
coord_fixed()

```

